\chapter{Introduction}
\section{Background}
In today's fast-paced world, people rely more on technology to plan their daily activities and
their free time. However, many planning tools provide general suggestions that may not be
suitable for individual preferences or specific situational requirements such as time, location, or
interest activities. The growing demand for personalized planning in mobile applications gives
an opportunity to create a smart solution that personalizes recommendations to each user's
specific preferences. Users today expect convenience, accuracy, and relevance, especially when
it comes to planning their day or deciding where to go for activities. Personalized services are no
longer an option but rather a requirement for improving user satisfaction and engagement in an
increasingly digital era.
\section{Objectivs}
\begin{enumerate}
    \item To provide the plan which is suitable to the user’s preference.
    \item To provide up-to-date information on opening hours and availability.
\end{enumerate}

\section{Scope}
This project aims to develop a mobile application that suggests one-day trip plans based on user
interests, such as cafes, restaurants, shopping, parks, and more. Users can also provide input,
such as starting location, date and time, and the number of places to visit, to refine the
suggestions and include more relevant locations in their plans. Users of the PlanADay
application
\begin{itemize}
    \item \textbf{can create} personalized one-day trip itineraries based on their interests and preferences.
    \item \textbf{can discover} nearby attractions that align with their preferences and current location.
    \item \textbf{can adjust} their generated plans by rearranging locations, deleting stops, or regenerating.
    \item \textbf{can view} detailed information for each suggested location.
    \item \textbf{can share} their trip plans with others on the platform.
    \item \textbf{can bookmark} plans created by other users for easy access and reference in the future.
    \item \textbf{can explore} their plan history to revisit past itineraries or gain inspiration for new trips.
\end{itemize}
\newpage

\section{Expected Benefits}
\begin{enumerate}
    \item \textbf{Seamless Trip Planning:} The main features of the application will help users to create
    their personal preferences, ensuring a tailored and enjoyable experience.
    \item \textbf{User Satisfaction and Flexibility:} Users will appreciate both the thoughtfully generated
    plans and the ease of customizing them to suit their needs, ensuring a more satisfying
    experience.
    \item \textbf{Business Partnerships:} By featuring related points of interest, such as shops and cafes,
    PlanADay opens opportunities for businesses to partner and connect with a highly
    engaged audience.
\end{enumerate}
